### 2025-08-29 sections/2-methods.tex
small mistake

The $\mathcal{O}(n\log n)$ build complexity assumes a balanced tree $\mathcal{T}$. In practice, Algorithm~\ref{alg:methods:partition} yields unbalanced trees on real data because of nonuniform sampling densities and the manifold’s low-dimensional structure. A balanced tree is expected only for uniformly distributed data (e.g., in a $d$-dimensional hypercube).

>>>>

The $\mathcal{O}(n\log n)$ build complexity assumes a balanced tree $\mathcal{T}$. In practice, our clustering algorithm yields unbalanced trees on real data because of nonuniform sampling densities and the manifold’s low-dimensional structure. A balanced tree is expected only for uniformly distributed data (e.g., in a $d$-dimensional hypercube).
